Ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2018-01-18 manuscript/usses_water_ms.Rmd
adds justification for dropping some control plots from community analysis; closes #14

Species composition data came from two sources: yearly census maps for each plot made using a pantograph [@Hill1920] and yearly counts of annual species in each plot.
\new{Mapping was done for plots within one of the permanent exclosures, which included six of the control plots and all of the treatment plots, for a total of 22 plots.}
From these sources, we determined the density of all annuals and perennials forbs, the basal cover of perennial grasses, and the canopy cover of shrubs.
We made a large plot-treatment-year by species matrix, where columns were filled with either basal cover or density, depending on the measurement made for the particular species.
We standardized the values in each column so we could directly compare species quantified with different metrics (density, basal cover, and canopy cover).
This puts all abundance values on the same scale, meaning that common and rare species are weighted equally.
Assuming that rare species will respond to treatments more than common ones, our approach is biased towards detecting compositional changes.

>>>>

Species composition data came from two sources: yearly census maps for each plot made using a pantograph [@Hill1920] and yearly counts of annual species in each plot.
From these sources, we determined the density of all annuals and perennials forbs, the basal cover of perennial grasses, and the canopy cover of shrubs.
We made a large plot-treatment-year by species matrix, where columns were filled with either basal cover or density, depending on the measurement made for the particular species.
We standardized the values in each column so we could directly compare species quantified with different metrics (density, basal cover, and canopy cover).
This puts all abundance values on the same scale, meaning that common and rare species are weighted equally.
Assuming that rare species will respond to treatments more than common ones, our approach is biased towards detecting compositional changes.
\new{We limited our community level data to observations from the permanent exclosure with our drought and irrigation treatments for the community composition analyses described below (\textbf{Community composition over time}).
This exclosure included six of the control plots and all of the treatment plots, for a total of 22 plots.
The other eight control plots are in other pastures, which would add a spatial bias to our community analysis focused on temporal dynamics.}

### 2018-01-18 manuscript/usses_water_ms.tex
adds justification for dropping some control plots from community analysis; closes #14

Species composition data came from two sources: yearly census maps for
each plot made using a pantograph \citep{Hill1920} and yearly counts of
annual species in each plot.
\new{Mapping was done for plots within one of the permanent exclosures, which included six of the control plots and all of the treatment plots, for a total of 22 plots.}
From these sources, we determined the density of all annuals and
perennials forbs, the basal cover of perennial grasses, and the canopy
cover of shrubs. We made a large plot-treatment-year by species matrix,
where columns were filled with either basal cover or density, depending
on the measurement made for the particular species. We standardized the
values in each column so we could directly compare species quantified
with different metrics (density, basal cover, and canopy cover). This
puts all abundance values on the same scale, meaning that common and
rare species are weighted equally. Assuming that rare species will
respond to treatments more than common ones, our approach is biased
towards detecting compositional changes.

>>>>

Species composition data came from two sources: yearly census maps for
each plot made using a pantograph \citep{Hill1920} and yearly counts of
annual species in each plot. From these sources, we determined the
density of all annuals and perennials forbs, the basal cover of
perennial grasses, and the canopy cover of shrubs. We made a large
plot-treatment-year by species matrix, where columns were filled with
either basal cover or density, depending on the measurement made for the
particular species. We standardized the values in each column so we
could directly compare species quantified with different metrics
(density, basal cover, and canopy cover). This puts all abundance values
on the same scale, meaning that common and rare species are weighted
equally. Assuming that rare species will respond to treatments more than
common ones, our approach is biased towards detecting compositional
changes.
\new{We limited our community level data to observations from the permanent exclosure with our drought and irrigation treatments for the community composition analyses described below (\textbf{Community composition over time}).
This exclosure included six of the control plots and all of the treatment plots, for a total of 22 plots.
The other eight control plots are in other pastures, which would add a spatial bias to our community analysis focused on temporal dynamics.}
